SunPy - Python for Solar Physics

### 2014-01-31 2-1-Map.tex
resolved argument
removed ack
Lots of minor edits

\subsection{Map}\label{ssec:map}
The map data type stores 2D spatial data, such as images of the Sun and 
inner heliosphere. It provides: a wrapper around a \texttt{numpy} data array; 
the images associated spatial coordinates; and other metadata. The \texttt{Map} 
class provides methods for typical operations on 2D data, such as rotation and 
re-sampling, as well as visualisation functionality.
The \texttt{Map} class also provides a convenient interface for loading data 
from a variety of sources, including a FITS file as shown in 
Listing~\ref{code:aia_1}.

The architecture of the map subpackage consists of a template map called
\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
\texttt{NDData} is a generic wrapper around a \texttt{numpy.ndarray} with a 
\texttt{meta} attribute to store metadata.
As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
not yet make full use of its capabilities, but this inheritance structure 
provides for future integration with \texttt{astropy}. In order to provide 
instrument- or detector-specific integration, \texttt{GenericMap} is designed
to be subclassed. Each subclass of \texttt{GenericMap} can register 
with the \texttt{Map} creation factory, which will then automatically return an instance
of the specific \texttt{GenericMap} subclass dependant upon the data provided. 
SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
instruments: 
\textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
\textit{STEREO}/EUVI and COR, \textit{Hinode}/XRT,
\textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
and \textit{IRIS} SJI frames. 
% RJH: Instruments should be consistent throughout (italics, caps, etc).  Also,
% usually citations are provided for instruments.
% dps: I would agree to add the citations if we were using the instrument in 
% the paper, but I don't think this is the case here.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> aiamap = sunpy.map.Map('aia_file.fits')
>>> smap = aiamap.submap([-1200, -200], [-1000, -0])
>>> smap.peek(draw_grid=True)
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
of the map is created and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

In addition to the data-type classes, the \texttt{map} sub-package provides two 
collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
temporally and spatially aligned data respectively.
\texttt{CompositeMap} provides methods for overlaying spatially aligned 
data, with support for visualisation of images and contour lines overlaid 
upon each other.
\texttt{MapCube} provides methods for animation of its series of \texttt{Map} 
objects. Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} show how to 
interact with these classes.

>>>>

\subsection{Map}\label{ssec:map}
The map data type stores 2D spatial data, such as images of the Sun and 
inner heliosphere. It provides: a wrapper around a \texttt{numpy} data array, 
the images associated spatial coordinates, and other metadata. The \texttt{Map} 
class provides methods for typical operations on 2D data, such as rotation and 
re-sampling, as well as visualisation functionality.
The \texttt{Map} class also provides a convenient interface for loading data 
from a variety of sources, including a FITS file as shown in 
Listing~\ref{code:aia_1}.

The architecture of the map subpackage consists of a template map called
\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
\texttt{NDData} is a generic wrapper around a \texttt{numpy.ndarray} with a 
\texttt{meta} attribute to store metadata.
As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
not yet make full use of its capabilities, but this inheritance structure 
provides for future integration with \texttt{astropy}. In order to provide 
instrument- or detector-specific integration, \texttt{GenericMap} is designed
to be subclassed. Each subclass of \texttt{GenericMap} can register 
with the \texttt{Map} creation factory, which will then automatically return an instance
of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
instruments: 
\textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
\textit{STEREO}/EUVI and COR, \textit{Hinode}/XRT,
\textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
and \textit{IRIS} SJI frames.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> aiamap = sunpy.map.Map('aia_file.fits')
>>> smap = aiamap.submap([-1200, -200], [-1000, -0])
>>> smap.peek(draw_grid=True)
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

In addition to the data-type classes, the \texttt{map} subpackage provides two 
collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
temporally and spatially aligned data respectively.
\texttt{CompositeMap} provides methods for overlaying spatially aligned 
data, with support for visualisation of images and contour lines overlaid 
upon each other.
\texttt{MapCube} provides methods for animation of its series of \texttt{Map} 
objects. Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} show how to 
interact with these classes.

### 2014-01-31 2-2-Lightcurve.tex
Lots of minor edits

Time series data and their analyses are a fundamental aspect of solar
physics for which many data sources are available.
SunPy provides a \texttt{LightCurve} class
with a convenient and consistent interface for handling solar time-series
data.  The main engine behind the \texttt{LightCurve} class is
the {\texttt{pandas}} data-analysis library, and 
\texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
object. The \texttt{pandas} library contains a large amount
of functionality for manipulating and analysing time-series data,
making it an ideal basis for \texttt{LightCurve} \citep{mckinney2012}.  \texttt{LightCurve}
assumes that the input data are time-ordered list(s) of numbers, and each
list becomes a column in the \texttt{pandas} DataFrame object.

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve} but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing a factory interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object sub-class provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.

A \texttt{LightCurve} object may be created using a number of different methods. 
For example, a \texttt{LightCurve} may be created for a specific instrument given
an input time range. In Listing~\ref{code:goes_lc}, 
the \texttt{LightCurve} constructor searches a remote source for the GOES X-ray 
data specified by the time interval, downloads the required files and 
subsequently creates and plots the object.

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
...                                         '2011-06-07 08:00')
>>> goes.peek()
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range, and the output of the 
\texttt{peek()} method.}
\label{code:goes_lc}
\end{listing}

Alternatively, if the data file already exists on the local system, the 
\texttt{Lightcurve} object may instead be initialised using that file as input.
Once the \texttt{Lightcurve} has been created, it may be manipulated in 
a variety of ways in order to perform time-series analysis.

>>>>

Time series data and their analyses are a fundamental part of solar
physics for which many data sources are available.
SunPy provides a \texttt{LightCurve} class
with a convenient and consistent interface for handling solar time-series
data.  The main engine behind the \texttt{LightCurve} class is
the {\texttt{pandas}} data-analysis library, and 
\texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
object. The \texttt{pandas} library contains a large amount
of functionality for manipulating and analysing time-series data,
making it an ideal basis for \texttt{LightCurve} \citep{mckinney2012}.  \texttt{LightCurve}
assumes that the input data are time-ordered list(s) of numbers, and each
list becomes a column in the \texttt{pandas} DataFrame object.

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve}, but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing a factory interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object subclass provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.

A \texttt{LightCurve} object may be created using a number of different methods. 
For example, a \texttt{LightCurve} may be created for a specific instrument given
an input time range. In Listing~\ref{code:goes_lc}, 
the \texttt{LightCurve} constructor searches a remote source for the GOES X-ray 
data specified by the time interval, downloads the required files, and 
subsequently creates and plots the object.

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
...                                         '2011-06-07 08:00')
>>> goes.peek()
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range and the output of the 
\texttt{peek()} method.}
\label{code:goes_lc}
\end{listing}

Alternatively, if the data file already exists on the local system, the 
\texttt{LightCurve} object may instead be initialised using that file as input.
Once the \texttt{LightCurve} object has been created, it may be manipulated in 
a variety of ways in order to perform time-series analysis.

### 2014-01-31 2-3-Spectra.tex
Lots of minor edits

\subsection{Spectra}\label{sec:spectra}
SunPy aims to provide broad support for solar spectroscopy
instruments.  The variety and complexity of these instruments and
their resultant datasets makes this a challenging goal.  The \texttt{spectra} module implements a
\texttt{Spectrum} class for 1D data (intensity as a function of frequency) and a
\texttt{Spectrogram} class for 2D data (intensity as a function of time and
frequency).  Each of these classes use a \texttt{numpy.ndarray} object
as its \texttt{data} attribute.  These two classes were implemented
with support from by the Astrophysics Research Group at Trinity
College Dublin, Ireland.
% schriste - is this necessary? surely we don't need to thank all of our employers

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.spectra.sources.callisto import CallistoSpectrogram
>>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T07:45:00"
>>> callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
>>> callisto_nobg = callisto.subtract_bg()
>>> callisto_nobg.peek(vmin = 0)
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{callisto_nobg}
\end{center}
\caption{Example of how \texttt{CallistoSpectrogram} retrieves the
  data for the requested time range and observatory, merges it and
  removes the background signal.  The data requested -- `BIR' -- is
  the code name of the \href{http://www.rosseobservatory.ie}{Rosse Observatory}
  at Birr Castle in Ireland.}
\label{code:spectra}
\end{listing}

>>>>

\subsection{Spectra}\label{sec:spectra}
SunPy aims to provide broad support for solar spectroscopy
instruments.  The variety and complexity of these instruments and
their resultant datasets makes this a challenging goal.  The \texttt{spectra} module implements a
\texttt{Spectrum} class for 1D data (intensity as a function of frequency) and a
\texttt{Spectrogram} class for 2D data (intensity as a function of time and
frequency).  Each of these classes uses a \texttt{numpy.ndarray} object
as its \texttt{data} attribute.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.spectra.sources.callisto import CallistoSpectrogram
>>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T07:45:00"
>>> callisto = CallistoSpectrogram.from_range("BIR", tstart, tend)
>>> callisto_nobg = callisto.subtract_bg()
>>> callisto_nobg.peek(vmin = 0)
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{callisto_nobg}
\end{center}
\caption{Example of how \texttt{CallistoSpectrogram} retrieves the
  data for the requested time range and observatory, merges it, and
  removes the background signal.  The data requested -- `BIR' -- is
  the code name of the \href{http://www.rosseobservatory.ie}{Rosse Observatory}
  at Birr Castle in Ireland.}
\label{code:spectra}
\end{listing}

### 2014-01-31 3-3-HELIO.tex
Lots of minor edits

The HELiophysics Integrated Observatory (HELIO\footnote{For more information 
see \url{http://helio-vo.eu}{http://helio-vo.eu}}) has 
compiled a list of web services which allows scientists to query and 
discover data throughout the heliosphere, from solar and magnetospheric data to planetary and 
inter-planetary data \citep{dps2012}.
HELIO is built with a Service-Oriented Architecture, 
i.e., its capabilities are divided into a number of tasks that are 
implemented as separate services. 
HELIO is made up of nine different public services, 
which allows scientists to search different catalogues of registered events, 
solar features, data from instruments in the heliosphere and other information 
such as planetary or spacecraft position in time. 
Additionally, HELIO provides a service that uses a 
propagation model to link the data in different points of the solar system by 
its original nature (e.g., Earth auroras are a signature of magnetic 
field disturbances produced few days before on the Sun).
In addition to the primary, web-based interface to 
HELIO, the services are available by API.

>>>>

The HELiophysics Integrated Observatory (HELIO)\footnote{For more information 
see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
compiled a list of web services which allows scientists to query and 
discover data throughout the heliosphere, from solar and magnetospheric data to planetary and 
inter-planetary data \citep{dps2012}.
HELIO is built with a Service-Oriented Architecture, 
i.e., its capabilities are divided into a number of tasks that are 
implemented as separate services. 
HELIO is made up of nine different public services, 
which allows scientists to search different catalogues of registered events, 
solar features, data from instruments in the heliosphere, and other information 
such as planetary or spacecraft position in time. 
Additionally, HELIO provides a service that uses a 
propagation model to link the data in different points of the solar system by 
its original nature (e.g., Earth auroras are a signature of magnetic 
field disturbances produced few days before on the Sun).
In addition to the primary, web-based interface to 
HELIO, the services are available by API.

### 2014-01-31 4-Util.tex
Lots of minor edits

\subsection{World Coordinate System (WCS) Coordinates}\label{ssec:util:wcs}
Coordinate transformations are frequently a necessary task within the solar 
data analysis workflow. Likely the most often used transformation is from 
observer coordinates (e.g., sky coordinates) to a coordinate system which is 
mapped onto the solar surface (e.g., latitude and longitude). This 
transformation is necessary to compare the true physical distance between 
different solar features. This type of transformation is not unique
to solar observations, but is not often considered by astronomical packages
such as the Astropy 
coordinates package. The \texttt{wcs} package in SunPy implements the World Coordinate 
System (WCS) for solar coordinates as described by \citep{thompson2006}. The 
transformations currently implemented are those most useful 
for most solar data analysis, namely converting from Helioprojective-Cartesian 
(HPC) to Heliographic (HG) coordinates. HPC describes the positions on 
the Sun as angles measured from the center of the solar disk (usually in 
arcseconds) using Cartesian coordinates (X, Y). This is the coordinate system 
most often defined in solar imaging data (see for example, images from 
\textit{SDO}/AIA, \textit{SOHO}/EIT, and \textit{TRACE}). 
HG coordinates express positions on the Sun using longitude and latitude on 
the solar sphere. There are two standards for this coordinate system:
Stonyhurst-Heliographic, where the origin is at the intersection of the solar 
equator and the central meridian as seen from Earth, and 
Carrington-Heliographic, which is fixed to the Sun and does not depend on Earth. The 
implementation of these transformations pass through a common coordinate system 
called Heliocentric-Cartesian (HCC), where positions are expressed in true 
(de-projected) physical distances instead of angles on the celestial sphere.
These transformations require some knowledge of the location of the observer 
which is usually provided by the image header. In the case where it is 
not, the observer is assumed to be at Earth. Listing \ref{code:wcs_code} shows 
some examples of coordinate transforms carried out in SunPy using the 
\texttt{wcs} utilities.

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import wcs
>>> wcs.convert_hg_hpc(10,53)
(100.49244115330731, 767.97438321917502)
# Convert that position back to heliographic coordinates
>>> wcs.convert_hpc_hg(100.49, 767.97)
(9.9996521808465175, 52.999563684874893)
# Try to convert a position which is not on the Sun to HG
>>> wcs.convert_hpc_hg(-1500,0)
sunpy/wcs/wcs.py:180: RuntimeWarning: invalid value encountered in sqrt
  distance = q - np.sqrt(distance)
(nan, nan)
Convert sky coordinate to a position in HCC
>>> wcs.convert_hpc_hcc(-300,400, z = True)
(-216716967.63331246, 288956420.9477042, 594364636.2208252)
\end{minted}
\caption{Using the \texttt{wcs} subpackage.}
\label{code:wcs_code}
\end{listing}

\subsubsection{Sun}\label{ssec:util:sun}
The purpose of the \texttt{sun} subpackage is to provide solar-specific data such as ephemerides and
solar constants. The main namespace contains a number of functions which provide solar
ephemerides such as the Sun to Earth distance, solar-cycle number, the mean 
anomaly, etc.
All of these functions take a time as their input which can be provided in a format
compatible with \texttt{sunpy.time.parse\_time()}. 
A future version of SunPy will integrate with the Astropy coordinates package and will 
likely make use of an ephemeris package.

The \texttt{sun.constants} module provides a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values both within the SunPy code base but also to the user. Every solar 
constant is provided as a \texttt{Constant} object as defined by Astropy. Each 
\texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
the constant's provenance (i.e., reference) as well as its uncertainty. Using 
Astropy's {Quantity} objects, any solar constant can easily be converted between 
different units as can be seen in Listing~\ref{code:constants_code} as well
as between the SI or cgs unit systems with a single command.  As these objects inherit from 
NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
For convenience a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.

@@

\subsubsection{Instruments}\label{ssec:util:inst}
In addition to providing support for instrument-specific solar data via the main data 
classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, 
some instrument-specific functions may be found within the \texttt{instr} subpackage. 
These functions are generally those that are unique to one particular solar instrument, 
rather than of general use, such as a function to construct a \textit{GOES} flare event list 
or a function to query the \textit{LYRA} timeline annotation file. Currently, some support is included
 for the \textit{GOES}, \textit{LYRA}, \textit{RHESSI} and \textit{IRIS} instruments, while future developments 
 will include support for additional missions. Ultimately, it is anticipated that solar
  missions requiring a large suite of software tools will be supported via a separately 
  maintained package that is affiliated with SunPy.

>>>>

\subsection{World Coordinate System (WCS) Coordinates}\label{ssec:util:wcs}
Coordinate transformations are frequently a necessary task within the solar 
data analysis workflow. Likely the most often used transformation is from 
observer coordinates (e.g., sky coordinates) to a coordinate system that is 
mapped onto the solar surface (e.g., latitude and longitude). This 
transformation is necessary to compare the true physical distance between 
different solar features. This type of transformation is not unique
to solar observations, but is not often considered by astronomical packages
such as the Astropy 
coordinates package. The \texttt{wcs} package in SunPy implements the World Coordinate 
System (WCS) for solar coordinates as described by \cite{thompson2006}. The 
transformations currently implemented are those most useful 
for most solar data analysis, namely converting from Helioprojective-Cartesian 
(HPC) to Heliographic (HG) coordinates. HPC describes the positions on 
the Sun as angles measured from the center of the solar disk (usually in 
arcseconds) using Cartesian coordinates (X, Y). This is the coordinate system 
most often defined in solar imaging data (see for example, images from 
\textit{SDO}/AIA, \textit{SOHO}/EIT, and \textit{TRACE}). 
HG coordinates express positions on the Sun using longitude and latitude on 
the solar sphere. There are two standards for this coordinate system:
Stonyhurst-Heliographic, where the origin is at the intersection of the solar 
equator and the central meridian as seen from Earth, and 
Carrington-Heliographic, which is fixed to the Sun and does not depend on Earth. The 
implementation of these transformations pass through a common coordinate system 
called Heliocentric-Cartesian (HCC), where positions are expressed in true 
(de-projected) physical distances instead of angles on the celestial sphere.
These transformations require some knowledge of the location of the observer, 
which is usually provided by the image header. In the cases where it is 
not provided, the observer is assumed to be at Earth. Listing \ref{code:wcs_code} shows 
some examples of coordinate transforms carried out in SunPy using the 
\texttt{wcs} utilities.

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import wcs
>>> wcs.convert_hg_hpc(10, 53)
(100.49244115330731, 767.97438321917502)
# Convert that position back to heliographic coordinates
>>> wcs.convert_hpc_hg(100.49, 767.97)
(9.9996521808465175, 52.999563684874893)
# Try to convert a position which is not on the Sun to HG
>>> wcs.convert_hpc_hg(-1500, 0)
sunpy/wcs/wcs.py:180: RuntimeWarning: invalid value encountered in sqrt
  distance = q - np.sqrt(distance)
(nan, nan)
Convert sky coordinate to a position in HCC
>>> wcs.convert_hpc_hcc(-300, 400, z=True)
(-216716967.63331246, 288956420.9477042, 594364636.2208252)
\end{minted}
\caption{Using the \texttt{wcs} subpackage.}
\label{code:wcs_code}
\end{listing}

\subsubsection{Sun}\label{ssec:util:sun}
The purpose of the \texttt{sun} subpackage is to provide solar-specific data such as ephemerides and
solar constants. The main namespace contains a number of functions that provide solar
ephemerides such as the Sun-to-Earth distance, solar-cycle number, the mean 
anomaly, etc.
All of these functions take a time as their input, which can be provided in a format
compatible with \texttt{sunpy.time.parse\_time()}. 
A future version of SunPy will integrate with the Astropy coordinates package and will 
likely make use of an ephemeris package.

The \texttt{sun.constants} module provides a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values  within the SunPy code base, but also to the user. Every solar 
constant is provided as a \texttt{Constant} object as defined by Astropy. Each 
\texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
the constant's provenance (i.e., reference) and its uncertainty. Using 
Astropy's \texttt{Quantity} objects, any solar constant can easily be converted between 
different units, including between the SI or cgs unit systems, as can be seen in Listing~\ref{code:constants_code}.
As these objects inherit from 
NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
For convenience, a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.

@@

\subsubsection{Instruments}\label{ssec:util:inst}
In addition to providing support for instrument-specific solar data via the main data 
classes \texttt{Map}, \texttt{LightCurve}, and \texttt{Spectrum}, 
some instrument-specific functions may be found within the \texttt{instr} subpackage. 
These functions are generally those that are unique to one particular solar instrument, 
rather than of general use, such as a function to construct a \textit{GOES} flare event list 
or a function to query the \textit{LYRA} timeline annotation file. Currently, some support is included
 for the \textit{GOES}, \textit{LYRA}, \textit{RHESSI} and \textit{IRIS} instruments, while future developments 
 will include support for additional missions. Ultimately, it is anticipated that solar
  missions requiring a large suite of software tools will each be supported via a separately 
  maintained package that is affiliated with SunPy.

### 2014-01-31 5-Dev.tex
Lots of minor edits

The continued success of an open-source project depends on many factors;
three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
active community \citep{bangerth2013}. Several tools (some specific to Python) are used by
SunPy to make achieving these goals more accessible. To maintain high-quality code, a 
transparent and collaborative development workflow made possible by GitHub is used.
The following conditions typically must be met before code is accepted.
\begin{enumerate}
	\item  The code must follow the
	\href{http://www.python.org/dev/peps/pep-0008/}{PEP 8} Python style 
	guidelines to maintain consistency in the SunPy code.

@@

High-quality documentation is
one of the most important factors determining the success of any software project. 
Powerful tools already exist in Python to support documentation, thanks to native
Python's focus on its own documentation. SunPy makes use of the Sphinx (\url{http://sphinx-doc.org})
documentation generator. Sphinx uses reStructuredText as its markup language, which is
an easy-to-read, what-you-see-is-what-you-get plaintext markup syntax. It supports
many output formats most notably HTML, as well as PDF and ePub, and provides a rich,
hierarchically structured view of in-code documentation strings. The SunPy documentation 
is built automatically and is hosted by Read-the 
-Docs (\url{http://readthedocs.org}) at \url{http://docs.sunpy.org}.

Communication is the key to maintaining an active community, and the SunPy community 
uses a number of different tools to facilitate communication. For immediate communications, an active IRC chat
room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
developer comments or discussions, an open mailing list is hosted by Google Groups. 
Bug tracking, code reviews, and feature-request discussions take place directly on GitHub.
The SunPy community also reaches out to the wider solar physics
community through presentations, functionality demonstrations and informal meetups at scientific
meetings.

>>>>

The continued success of an open-source project depends on many factors;
three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
active community \citep{bangerth2013}. Several tools, some specific to Python, are used by
SunPy to make achieving these goals more accessible. To maintain high-quality code, a 
transparent and collaborative development workflow made possible by GitHub is used.
The following conditions typically must be met before code is accepted.
\begin{enumerate}
	\item  The code must follow the
	\href{http://www.python.org/dev/peps/pep-0008/}{PEP 8} Python style 
	guidelines to maintain consistency in the SunPy code.

@@

High-quality documentation is
one of the most important factors determining the success of any software project. 
Powerful tools already exist in Python to support documentation, thanks to native
Python's focus on its own documentation. SunPy makes use of the Sphinx (\url{http://sphinx-doc.org})
documentation generator. Sphinx uses reStructuredText as its markup language, which is
an easy-to-read, what-you-see-is-what-you-get plaintext markup syntax. It supports
many output formats most notably HTML, as well as PDF and ePub, and provides a rich,
hierarchically structured view of in-code documentation strings. The SunPy documentation 
is built automatically and is hosted by Read-the-Docs (\url{http://readthedocs.org})
at \url{http://docs.sunpy.org}.

Communication is the key to maintaining an active community, and the SunPy community 
uses a number of different tools to facilitate communication. For immediate communications, an active IRC chat
room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
developer comments or discussions, an open mailing list is hosted by Google Groups. 
Bug tracking, code reviews, and feature-request discussions take place directly on GitHub.
The SunPy community also reaches out to the wider solar physics
community through presentations, functionality demonstrations, and informal meetups at scientific
meetings.
